SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-09 maintex.tex
Updated Results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}). The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. Inside and outside-IFU pairs are marked with {\it grey diamonds}. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial Profiles of Star Formation}\label{sec:analysis}

\subsection{Specific Star Formation Rate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles). The colors of the profiles represent the mass range of the selected galaxies and the highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.}
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Once the geometry of the galaxies are set, we can build the radial profiles. The spaxels are binned into radius increments of 0.1 R/\reff\ from 0.0$-$2.5 R/\reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We create one of these individual averaged radial profiles for every MaNGA galaxy.

We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data. Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog. This gives us an individual radial profile of the sSFR for all paired and control galaxies.

@@

@@

The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region. A radial bin is trimmed if less than 70\% of the galaxies in that bin have data. There are a few reasons why galaxy's profile may not have data points at a given radial bin. First, the MaNGA IFU may not cover the radius range; only $\sim$37\% of MaNGA galaxies are covered out to 2.5 $R$/\reff. This radial coverage limitation primarily affect the lower mass galaxies in the \logm\ $=$ 9.0$-$9.5. Second, foreground and background objects have been masked out which can create gaps in the data of an individual galaxies profile. This case does not significantly affect the stacked profiles here since the masked out regions will be spread out across the whole radius range. Third, retired regions within galaxies have been masked out with the \ewha\ $\ge$ 3\AA\ cut. It is well known that high mass galaxies tend to be passive (as seen in our CMD diagram in Figure \ref{fig:cmd}). As a consequence, the highest mass galaxies in our sample (\logm\ $=$ 11.0$-$11.5) have much of their profiles trimmed due to absence of star forming spaxels.

This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls. On the other hand, this method only controls for a single galaxy parameter, stellar mass. Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.

The profiles of the control galaxies are centrally quenched, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}. The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $=$ 10.5 which show some central quenching. When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex. This enhancement linearly falls to zero around 1.0 $R$/\reff. In the disks the profiles feature a weak suppression to the sSFR of 0.05$-$0.1 dex.

The sSFR in the pair sample shows no dependence on their stellar mass. The profiles from all of the mass ranges fall within $\sim$0.2 of the median profile. This means that low mass galaxies are enhanced at the same level as high mass galaxies. It is also notable that while this method of pair-control comparison is not rigorous as the next method, the central star formation enhancement is clearly present at all stellar masses.

@@

@@

Once the average profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the average control profile in log space. We do this process for each of the 175 paired galaxies.

@@

The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex. The enhancement falls to zero around 1.0 \reff\ and is slightly suppressed in their disks by $\sim$0.1 dex. While all of the other paired galaxies show a sSFR suppression in their disks, the profiles of the pairs in the stellar mass range of \logm\ $=$ 9.0$-$9.5 show an enhancement in their disks of $\sim$0.1$-$0.2 $\pm$ 0.1 dex.

The profiles are largely consistent with the results of the previous mass binning method. The profiles of this method have less scatter as a result of how the paired are more closely matched in stellar mass and redshift. This method also has the added benefit that the profiles can be separated by parameters other than stellar mass. We will discuss how these profiles behave as a function of the mass ratio and projected separation in the following sections.

We can also inspect the star formation enhancement within individual paired galaxies. We extract the $\Delta$log(sSFR) from the individual difference profiles. We extract the value of $\Delta$log(sSFR) from the inner 0.5 $R$/\reff\ of the paired galaxies and take the mean value of the $\Delta$log(sSFR) within the aperture. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}. The mass independence can be clearly seen here as the paired galaxies within each stellar mass bin fall within 0.1 dex of the 0.2 dex $\Delta$log(sSFR) median.

Between the two different pair-control comparison methods, we conclude that the $\Delta$log(sSFR) is independent of the paired galaxies' stellar mass. Low mass galaxies are having their sSFR enhanced at a similar rate as high mass galaxies.

%\subsection{Future Mass Growth}

%The higher rate of star formation within interacting galaxies will mean that the stellar mass in the interacting galaxies will grow at a faster rate compared to secular mass growth. The question is whether or not the advanced mass growth rate is significant.

%To estimate the enhanced mass growth rate due to merger induced star formation, we will assume a constant star formation rate over a given timescale, $\tau$. A specific star formation rate is already a representation of the fractional mass growth every year, so the merger induced mass growth is simply;

%\begin{equation}
%\frac{\Delta M_{merger}}{M_{total}} = \left({\rm sSFR}_{\rm pair} - {\rm sSFR}_{\rm control}\right) * \tau
%\end{equation}

%For this estimation we use a timescale of 1 Gyr, which is the order of the typical timescale between the passage of the first and second pericenters in dark-matter simulations \citep{Boylan-Kolchin:2008}. The actual timescale for star formation enhancement is likely shorter; however, we will use the 1 Gyr value as an order of magnitude estimate.

%To get the difference in sSFR between the pairs and controls, we fit a gaussian to the difference profiles split by stellar mass. We then add the modeled difference profile to the stacked control profile in the same mass range in log space. We then take the difference between the profiles in linear space and multiply the difference by the 1 Gyr timescale.

%We show the mass growth rate profile for each of the four mass ranges in Figure \ref{fig:mass_gain_sum}. The mass growth rate is largely restricted to the centers of the galaxies and falls to zero around 1.0 R/\reff, following profile of the $\Delta$log(sSFR). The mass growth rate is strongly dependent on the stellar mass of the paired galaxies.

%The fractional mass change is greatest in the less massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.06 (6\%), while it is less substantial is the more massive galaxies, $\Delta$M$_{merger}$/M$_{total}$ $=$ 0.005 (0.5\%). This is unsurprising as the $\Delta$log(sSFR) profiles were independent of the galaxies' total stellar mass.

%In the context of galaxy evolution, where less massive galaxies merge to form larger galaxies, the merger induced star formation contributes a significant amount of stellar mass on top of the stellar mass contribution from the mixing of the two galaxies. Further, the merger induced mass growth is restricted to the centers of the paired galaxies which will result in galaxies which have more prominent bulges in their centers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Dependency on Mass Ratio}
While the total stellar mass of the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does. The mass ratio here is calculated as the difference between stellar masses contained within the 50\% half light radius,

@@

Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy.

@@

In the Top row of Figure \ref{fig:ssfr_dmsep} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0.

We also use the mass ratio to explore how the merger induced tidal torques affect paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ > 0.5. We use the mass ratio to separate the massive central galaxy from satellite galaxies. A paired galaxy with a positive mass ratio is the more massive galaxy of the pair while a paired galaxy with negative mass ratio is the less massive galaxy. We see that the less massive galaxy of a pair show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to the more massive galaxy. This shows us that satellite galaxies may be more susceptible to tidal interactions than the central galaxies in the pair system.

In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}. We see the same effect; however, we have also found that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement. It has been a convention to split galaxy pairs in major mergers, $|$log($M$)$|$ $\le$ 0.5, and minor mergers 0.5 $<$ $|$log($M$)$|$ $\le$ 1.0. In this work, we can see that the mass ratio range used in galaxy pair studies could be widened to at least $|$log($M$)$|$ $\le$ 1.5 so that larger pair samples can be constructed.

Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair ($\Delta$log($M$) $<$ 0) shows higher levels of sSFR enhancement. This implies that satellite galaxies are more affected by interaction induced star formation than the central galaxy.

@@

We also look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in the bottom row of Figure \ref{fig:ssfr_dmsep}. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.1 dex below the median.

@@

For galaxies with separations of $r_{\rm p}$ $<$ 5 kpc and $r_{\rm p}$ $=$ 30$-$35 kpc we find a $\Delta$log(sSFR) of zero. For the $r_{\rm p}$ $<$ 5 kpc galaxies, about half of the pairs show signs of tidal features while the others do not. The pairs without the tidal features may be approaching their first pericenter, meaning that the merger-induced gas-inflows have not been triggered yet. The dips in $\Delta$log(sSFR) may also just be due to statistical error from the relatively limited sample size.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec:disc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}
%\centering
%\includegraphics[width=3in]{fig/mass_gain.pdf}
%\caption[The fractional mass gain due to merger induced star formation.]{The fractional mass growth due to merger induced star formation over 1 Gyr. The highlighted region represents the propagated standard errors of the mean of the stacked log(sSFR) profiles. }
%\label{fig:mass_gain_sum}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_partial.pdf}
\caption[]{{\it Use larger bins here.} Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio (\textbf{Top row}) and projected separation (\textbf{Bottom row}). }
\label{fig:ssfr_dmsep}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/nuc_sep.pdf}
\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple). (\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).  }
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. Inside-IFU pairs are marked with red diamonds and the outside-IFU pairs are marked with red squares. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial Profiles of Star Formation}\label{sec:analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. The parts of the profiles with dashed lines represent regions where less than 50\% of the galaxies in the bin are covered at that radii. }
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Specific Star Formation Rate}

@@

@@

Once the geometry of the galaxies are set, we can build the radial profiles. The spaxels are binned into radius increments of 0.2 R/\reff\ from 0.0$-$2.6 R/\reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We create one of these individual averaged radial profiles for every MaNGA galaxy.

%We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foreground/background objects within the MaNGA IFUs which may contaminate the data. Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 R/\reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog. This gives us an individual radial profile of the sSFR for all paired and control galaxies.

@@

The radial extent of our profiles go out to 2.6 $R$/\reff; however,  67\% of the MaNGA sample is designed to cover only 1.5 $R$/\reff\ of the galaxy. Also, the MaNGA galaxies are not always centered on a spaxel center, so the 0$^{\rm th}$ spaxel may fall into the 0.2 $R$\reff\ bin. Because of these issues, the centers or the outskirts of the stacked profiles may only represent a small subset of the galaxies in that mass bin. To account for this, we ``trim" the stacked profiles where radii bins contain data for less than 50\% of the total set of galaxies. We represent the trimmed regions in our figures with dashed lines. In Figure \ref{fig:ssfr_prof}, this is shown in the centers of the lower mass galaxies, \logm\ $\le$ 10.0.

@@

%The dashed regions of the profiles in Figure \ref{fig:ssfr_prof} represent regions which have been ``trimmed" due to a low percent of data coverage in the region. A radial bin is trimmed if less than 70\% of the galaxies in that bin have data. There are a few reasons why galaxy's profile may not have data points at a given radial bin. First, the MaNGA IFU may not cover the radius range; only $\sim$37\% of MaNGA galaxies are covered out to 2.5 $R$/\reff. This radial coverage limitation primarily affect the lower mass galaxies in the \logm\ $=$ 9.0$-$9.5. Second, foreground and background objects have been masked out which can create gaps in the data of an individual galaxies profile. This case does not significantly affect the stacked profiles here since the masked out regions will be spread out across the whole radius range. Third, retired regions within galaxies have been masked out with the \ewha\ $\ge$ 3\AA\ cut. It is well known that high mass galaxies tend to be passive (as seen in our CMD diagram in Figure \ref{fig:cmd}). As a consequence, the highest mass galaxies in our sample (\logm\ $=$ 11.0$-$11.5) have much of their profiles trimmed due to absence of star forming spaxels.

The profiles of the control galaxies are lower in their centers, which was previously seen in the MaNGA sample in \citet{Belfiore:2018}. The profiles of the paired galaxies flat across the whole galaxy accept for galaxies with masses above \logm\ $\ge$ 10.5 which show some central quenching. Because of this, it may be more accurate to describe the control galaxies as centrally suppressed or quenched in comparison to the paired galaxies which feature flat profiles of star formation. The difference in the pair and control profiles seems to indicate that the mechanism for quenching in galaxies is the depletion of gases in their centers. The gas inflows from the merger events can then refuel the centers of these quenched galaxies and allow new star formation to occur.

When taking the difference between the pairs and controls, the paired profiles are centrally enhanced by $\sim$0.35 $\pm$ 0.1 dex which then falls to zero around 1.2 R/\reff. In the outskirts of the pairs beyond 1.2 R/\reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. The most massive galaxies in the range, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 R/\reff\ is higher than the median profile at 0.5$-$0.6 dex. The sSFR enhancement in the sample seems to mass independent except for the most massive galaxies which feature higher levels of enhancement.

@@

This method has the benefit of a high S/N control profile since each mass bin will have hundreds of control galaxies while the median control profiles of the second method will only have 20 controls. On the other hand, this method only controls for a single galaxy parameter, stellar mass, though it is still relevant that the central enhancement of the sSFR in pairs is able to be observed. Further the profiles can only be studied as a function of stellar mass so we are unable to study the profiles as a function of projected separation or mass ratio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/sep_hist.pdf}
\caption[]{The projected separation distribution of the whole sample (blue) against the projected separation distribution for the highest mass galaxies, \logm\ $=$ 11.0$-$11.5 (Red). }
\label{fig:sep_hist}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Once the median profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the median control profile in log space. We do this process for each of the 175 paired galaxies.

@@

To focus on the sSFR offsets in the centers of the galaxies, we take the median sSFR within 0.5 \reff\ for all galaxies. We then calculate the offsets in the centers of the pairs by taking the difference between the sSFR in the centers of the pairs and the median sSFR of their 20 controls. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}

The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex. Similar to what was seen in Section \ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.

To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation between the whole sample and the galaxies in the highest mass bin in Figure \ref{fig:sep_hist}. The whole sample has a relatively flat separation distribution while 70\% of the highest mass galaxies in the sample are within 20 kpc. As we will show in Section \ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.

The central enhancement to the sSFR falls to zero around 1.2 $R$/\reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex. The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex. As we will show in the next section, Section \ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.

The results we obtain from the tailored-control method is largely consistent with the mass-binning method. Between the two methods we see that the $\Delta$log(sSFR) profile is independent of the total stellar mass of the galaxies. In the next two sections, we will use the tailored-control method to study how the profiles behave as a function of the mass ratio (Section \ref{sec:dm}) and projected separation (Section \ref{sec:sep}).

\subsection{Dependency on Mass Ratio}\label{sec:dm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\centering
%\includegraphics[width=\linewidth]{fig/ssfr_massdm.pdf}
%\caption[]{Same as the left hand panel of Figure \ref{fig:ssfr_mass} except primary companions are shown on the \textbf{Left} and secondary companions are shown on the \textbf{Right}. The \logm\ $=$ 11.0$-$11.5 mass bin is left out of left hand panel since it only contains two galaxies. }
%\label{fig:ssfr_massdm}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

While the total stellar mass of the galaxies has no effect on the merger induced star formation, the mass ratio between the paired galaxies does. The mass ratio here is calculated as the difference between stellar masses contained within the 50\% half light radius,

@@

Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We will define the more massive galaxies of a pair, $\Delta$log(M) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log(M) $<$ 0.0, the secondary companion.

@@

In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log(M)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log(M)$|$ $>$ 0.5. Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex. Secondary companions also feature slightly higher levels of enhancement than primary companions at the same mass ratios by $\sim$0.1 dex.

The sSFR offsets in the outskirts of the galaxy pairs show a dependence on the mass ratio. Primary companions show a zero to positive enhancement, 0.0$-$ 0.4 dex, to the sSFR in their outskirts. Secondary companions feature a suppression to the sSFR in their outskirts of about 0.1$-$0.4 dex.

In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0. We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.

%To emphasize the difference between primary and secondary companions and to further investigate the sSFR enhancement seen in the outskirts of low mass galaxies (\logm\ $=$ 9.0$-$9.5), we plot the difference profiles split both by stellar mass and mass ratio in Figure \ref{fig:ssfr_massdm}. The difference profile of primary companions is centrally enhanced by 0.25 dex and remains enhanced across their disks with an enhancement of 0.1-0.3 dex. The difference profile of secondary companions is centrally enhanced by 0.3 dex and is suppressed by 0.1 dex in their outskirts. Specifically looking at the paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, the primary companions in the mass range show strong enhancements to their outskirts while the primary companions in the mass range show a weak suppression to their outskirts.

From the mass ratio, we see two different effects. First, we see that the central enhancement to the sSFR is strongest for pairs with 1:1 mass ratios. Second, we see that secondary companions show steeper enhancement profiles with higher levels of sSFR enhancement in their centers and stronger sSFR suppression in their disks with respect to primary companions. It is interesting to note that the central enhancement to sSFR is dependent on both the mass ratio and the projected separation (which we will demonstrate in the next section) while the sSFR offsets in their outskirts primarily depends on whether the galaxy is the primary or secondary companion of the pair.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_sep.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by projected separation. }
\label{fig:ssfr_sep}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We look at the level of sSFR enhancement as a function of the projected separation between the two galaxies in Figure \ref{fig:ssfr_sep}. The $\Delta$log(sSFR) profiles show a clear gradient with the projected separation where close galaxy pairs show higher levels of sSFR enhancement compared to pairs with wide separations. The profiles in the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 0.0$-$12.5, are generally $\sim$0.05$-$0.1 dex above the median and the profiles of the galaxy pairs in the separation range, $r_{\rm p}$ $=$ 37.5$-$50.0, are generally $\sim$0.05$-$0.1 dex below the median.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec:disc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method (Black) compared against those of \citet{Pan:2019} (Red) and \citet{Thorp:2019} (Blue).}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/nuc_sep.pdf}
\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample using the tailored control method (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple). (\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).  }
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
